---
title: "pi_curves_nls"
author: "Ariana S Huffmyer"
date: "3/18/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message = FALSE, warning = FALSE)
```

```{r load_packages}
#Read in required libraries
library("devtools")
library("ggplot2")
library("segmented")
library("plotrix")
library("gridExtra")
library("lubridate")
library("chron")
library("plyr")
library("dplyr")
library("tidyr")
library("tidyverse")
library("broom")
library("ggpubr")
library("minpack.lm")
library("ggpmisc")

```

Load metadata
```{r}
sample.info <- read.csv("RAnalysis/data/Spat_Info.csv", na.strings = "NA")
sample.info$Size.mm2 <- as.numeric(as.character(sample.info$Size.mm2))

#Plot Size as a function of Polyp Number
ggplot(data = sample.info, aes(x = Polyp.Number, y = Size.mm2)) +
  stat_poly_line() +
  stat_poly_eq(use_label(c("eq", "R2","P")), size = 4) +
  geom_point() +
  theme_classic()
```

PLATE1
# Import data
```{r import_data}
Data <-read.csv("/Users/hputnam/Downloads/plate_4_ASF.csv", header=T, sep=";", na.string="NA") #reads in the data files
Data <- Data[, c("Date", "Time", "PAR", "ETR1","ETR2","ETR3","ETR4")]
# change format from wide to long
Data <- Data %>%  pivot_longer(., cols = starts_with("ETR"), names_to = "Spat.ID")
Data$value <- na_if(Data$value, 0)
#need to Remove all data at PAR values above where ETR hits zero
Data$PAR <- as.numeric(Data$PAR)
colnames(Data)[5] ="ETR"

```


# View Data plots
```{r}
Data <- Data %>%
  subset(ETR<40)

Data %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point()+
  geom_line()+
  facet_wrap("Spat.ID")
  theme_bw()

```

```{r}
set.seed(123)
Data.PI <- Data %>% subset(PAR<900) 
curve.nlsPIC <- Data.PI %>% nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))
coef(curve.nlsPIC)
plot(ETR ~ PAR, data = Data.PI)
lines(0:900,
      predict(curve.nlsPIC,
              newdata = data.frame(PAR = 0:900)))
```
# Define PI curve function as a nonlinear Least Squares regression of a quadratic fit, test nls fit
Aquatic Photosynthesis, Falkowski   
Pmax = max photosynthesis (AKA Am from Bayesian script)  
alpha = quantum yeild (AKA AQY from Bayesian script)  
I/E = irradiance (AKA PAR from Bayesian script)  
Rd = dark respiration   

Using fixed initial values (keeping for reference):  
```{r}

# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR13"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR16"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR19"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR2"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR7"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR1"))

nls_data1 <- Data.PI %>%
group_by(Spat.ID) %>%
nest(-Spat.ID) %>%
mutate(model1 = map(data, ~
nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4)) %>%
tidy %>%
dplyr::select(term, estimate) %>%
spread(term, estimate))) %>%
unnest(model1) %>%
mutate(Ik = Am/AQY)%>%
mutate(Date = "20230505") %>%
mutate(Plate = "Plate1") %>%
mutate(Spat.ID.PAM = paste0(Date,"_",Plate,"_",Spat.ID)) #%>%
#write_csv(., "RAnalysis/output/Plate1_pi_curve_pars_NLS_fixedparms.csv")
```

Plot curve over data points.  
```{r}
augmented <- Data.PI %>%
  filter(PAR <900) %>%
  nest(-Spat.ID) %>% 
  mutate(
    fit = map(data, ~ nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))),
    augmented = map(fit, augment),
  ) %>% 
  unnest(augmented)

augmented$ID <-augmented$Spat.ID
Aug <- augmented %>% separate(ID, c("Sp", "Num", "Type"))

#all colonies together
pdf("RAnalysis/output/Plate1_PI_Curve_Fit_Plots.pdf")
PI.curves <- Aug %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point() + 
  geom_line(aes(y=.fitted, x=PAR,group=Spat.ID))+
  theme_classic()+
          labs(x = expression(paste('PAR (', mu, "mol photons m"^-2, 's'^-1,")")),
               y = expression(paste("ETR")))+
  theme(legend.position = "top")
PI.curves
dev.off()

```
#PLATE 2

# Import data
```{r import_data}
Data <-read.csv("RAnalysis/data/ImagingPam/20230505_Spat_Plate2_newpoi.csv", header=T, sep=";", na.string="NA") #reads in the data files
Data <- Data[, c("Date", "Time", "PAR", "ETR1","ETR2","ETR3","ETR4","ETR5","ETR6","ETR7","ETR8","ETR9","ETR10","ETR11",
      "ETR12","ETR13","ETR14","ETR15","ETR16","ETR17","ETR18",
      "ETR19","ETR20","ETR21","ETR22")]
# change format from wide to long
Data <- Data %>%  pivot_longer(., cols = starts_with("ETR"), names_to = "Spat.ID")
Data$value <- na_if(Data$value, 0)
#need to Remove all data at PAR values above where ETR hits zero
Data$PAR <- as.numeric(Data$PAR)
colnames(Data)[5] ="ETR"

```


# View Data plots
```{r}
Data %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point()+
  theme_bw()
```

```{r}
set.seed(123)
Data.PI  <- Data %>% subset(PAR<900) 
curve.nlsPIC <- Data.PI %>% nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))
coef(curve.nlsPIC)
plot(ETR ~ PAR, data = Data.PI)
lines(0:900,
      predict(curve.nlsPIC,
              newdata = data.frame(PAR = 0:900)))
```
# Define PI curve function as a nonlinear Least Squares regression of a quadratic fit, test nls fit
Aquatic Photosynthesis, Falkowski   
Pmax = max photosynthesis (AKA Am from Bayesian script)  
alpha = quantum yeild (AKA AQY from Bayesian script)  
I/E = irradiance (AKA PAR from Bayesian script)  
Rd = dark respiration   

Using fixed initial values  
```{r}

Data.PI <- Data.PI %>% subset(Spat.ID!="ETR12")
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR13"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR18"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR19"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR6"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR7"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR9"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR18"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR19"))

nls_data2 <- Data.PI %>%
group_by(Spat.ID) %>%
nest(-Spat.ID) %>%
mutate(model1 = map(data, ~
nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4)) %>%
tidy %>%
dplyr::select(term, estimate) %>%
spread(term, estimate))) %>%
unnest(model1) %>%
mutate(Ik = Am/AQY)%>%
mutate(Date = "20230505") %>%
mutate(Plate = "Plate2") %>%
mutate(Spat.ID.PAM = paste0(Date,"_",Plate,"_",Spat.ID)) %>%
write_csv(., "RAnalysis/output/Plate2_pi_curve_pars_NLS_fixedparms.csv")
```

Plot curve over data points.  
```{r}
augmented <- Data.PI %>%
  filter(PAR <900) %>%
  nest(-Spat.ID) %>% 
  mutate(
    fit = map(data, ~ nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))),
    augmented = map(fit, augment),
  ) %>% 
  unnest(augmented)

augmented$ID <-augmented$Spat.ID
Aug <- augmented %>% separate(ID, c("Sp", "Num", "Type"))

#all colonies together
pdf("RAnalysis/output/Plate2_PI_Curve_Fit_Plots.pdf")
PI.curves <- Aug %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point() + 
  geom_line(aes(y=.fitted, x=PAR,group=Spat.ID))+
  theme_classic()+
          labs(x = expression(paste('PAR (', mu, "mol photons m"^-2, 's'^-1,")")),
               y = expression(paste("ETR")))+
  theme(legend.position = "top")
PI.curves
dev.off()

```

#PLATE 3

# Import data
```{r import_data}
Data <-read.csv("RAnalysis/data/ImagingPam/20230510_Spat_Plate3.csv", header=T, sep=";", na.string="NA") #reads in the data files
Data <- Data[, c("Date", "Time", "PAR", "ETR1","ETR2","ETR3","ETR4","ETR5","ETR6","ETR7","ETR8","ETR9","ETR10","ETR11",
      "ETR12","ETR13","ETR14","ETR15","ETR16","ETR17","ETR18",
      "ETR19","ETR20","ETR21","ETR22")]
# change format from wide to long
Data <- Data %>%  pivot_longer(., cols = starts_with("ETR"), names_to = "Spat.ID")
Data$value <- na_if(Data$value, 0)
#need to Remove all data at PAR values above where ETR hits zero
Data$PAR <- as.numeric(Data$PAR)
colnames(Data)[5] ="ETR"

```


# View Data plots
```{r}
Data %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point()+
  theme_bw()
```

```{r}
set.seed(123)
Data.PI  <- Data %>% subset(PAR<900) 
curve.nlsPIC <- Data.PI %>% nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))
coef(curve.nlsPIC)
plot(ETR ~ PAR, data = Data.PI)
lines(0:900,
      predict(curve.nlsPIC,
              newdata = data.frame(PAR = 0:900)))
```
# Define PI curve function as a nonlinear Least Squares regression of a quadratic fit, test nls fit
Aquatic Photosynthesis, Falkowski   
Pmax = max photosynthesis (AKA Am from Bayesian script)  
alpha = quantum yeild (AKA AQY from Bayesian script)  
I/E = irradiance (AKA PAR from Bayesian script)  
Rd = dark respiration   

Using fixed initial values  
```{r}

Data.PI <- Data.PI %>% subset(Spat.ID!="ETR1")
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR14"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR17"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR19"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR4"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR6"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR9"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR18"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR19"))

nls_data3 <- Data.PI %>%
group_by(Spat.ID) %>%
nest(-Spat.ID) %>%
mutate(model1 = map(data, ~
nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4)) %>%
tidy %>%
dplyr::select(term, estimate) %>%
spread(term, estimate))) %>%
unnest(model1) %>%
mutate(Ik = Am/AQY)%>%
mutate(Date = "20230510") %>%
mutate(Plate = "Plate3") %>%
mutate(Spat.ID.PAM = paste0(Date,"_",Plate,"_",Spat.ID)) %>%
write_csv(., "RAnalysis/output/Plate3_pi_curve_pars_NLS_fixedparms.csv")
```

Plot curve over data points.  
```{r}
augmented <- Data.PI %>%
  filter(PAR <900) %>%
  nest(-Spat.ID) %>% 
  mutate(
    fit = map(data, ~ nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))),
    augmented = map(fit, augment),
  ) %>% 
  unnest(augmented)

augmented$ID <-augmented$Spat.ID
Aug <- augmented %>% separate(ID, c("Sp", "Num", "Type"))

#all colonies together
pdf("RAnalysis/output/Plate3_PI_Curve_Fit_Plots.pdf")
PI.curves <- Aug %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point() + 
  geom_line(aes(y=.fitted, x=PAR,group=Spat.ID))+
  theme_classic()+
          labs(x = expression(paste('PAR (', mu, "mol photons m"^-2, 's'^-1,")")),
               y = expression(paste("ETR")))+
  theme(legend.position = "top")
PI.curves
dev.off()

```


#PLATE 4

# Import data
```{r import_data}
Data <-read.csv("RAnalysis/data/ImagingPam/20230510_Spat_Plate4.csv", header=T, sep=";", na.string="NA") #reads in the data files
Data <- Data[, c("Date", "Time", "PAR", "ETR1","ETR2","ETR3","ETR4","ETR5","ETR6","ETR7","ETR8","ETR9","ETR10","ETR11",
      "ETR12","ETR13","ETR14","ETR15","ETR16","ETR17","ETR18",
      "ETR19","ETR20","ETR21","ETR22")]
# change format from wide to long
Data <- Data %>%  pivot_longer(., cols = starts_with("ETR"), names_to = "Spat.ID")
Data$value <- na_if(Data$value, 0)
#need to Remove all data at PAR values above where ETR hits zero
Data$PAR <- as.numeric(Data$PAR)
colnames(Data)[5] ="ETR"

```


# View Data plots
```{r}
Data %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point()+
  theme_bw()
```

```{r}
set.seed(123)
Data.PI  <- Data %>% subset(PAR<900) 
curve.nlsPIC <- Data.PI %>% nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))
coef(curve.nlsPIC)
plot(ETR ~ PAR, data = Data.PI)
lines(0:900,
      predict(curve.nlsPIC,
              newdata = data.frame(PAR = 0:900)))
```
# Define PI curve function as a nonlinear Least Squares regression of a quadratic fit, test nls fit
Aquatic Photosynthesis, Falkowski   
Pmax = max photosynthesis (AKA Am from Bayesian script)  
alpha = quantum yeild (AKA AQY from Bayesian script)  
I/E = irradiance (AKA PAR from Bayesian script)  
Rd = dark respiration   

Using fixed initial values  
```{r}

Data.PI <- Data.PI %>% subset(Spat.ID!="ETR19")
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR2"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR20"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR7"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR4"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR6"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR9"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR18"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR19"))

nls_data4 <- Data.PI %>%
group_by(Spat.ID) %>%
nest(-Spat.ID) %>%
mutate(model1 = map(data, ~
nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4)) %>%
tidy %>%
dplyr::select(term, estimate) %>%
spread(term, estimate))) %>%
unnest(model1) %>%
mutate(Ik = Am/AQY)%>%
mutate(Date = "20230510") %>%
mutate(Plate = "Plate4") %>%
mutate(Spat.ID.PAM = paste0(Date,"_",Plate,"_",Spat.ID)) %>%
write_csv(., "RAnalysis/output/Plate4_pi_curve_pars_NLS_fixedparms.csv")
```

Plot curve over data points.  
```{r}
augmented <- Data.PI %>%
  filter(PAR <900) %>%
  nest(-Spat.ID) %>% 
  mutate(
    fit = map(data, ~ nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))),
    augmented = map(fit, augment),
  ) %>% 
  unnest(augmented)

augmented$ID <-augmented$Spat.ID
Aug <- augmented %>% separate(ID, c("Sp", "Num", "Type"))

#all colonies together
pdf("RAnalysis/output/Plate4_PI_Curve_Fit_Plots.pdf")
PI.curves <- Aug %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point() + 
  geom_line(aes(y=.fitted, x=PAR,group=Spat.ID))+
  theme_classic()+
          labs(x = expression(paste('PAR (', mu, "mol photons m"^-2, 's'^-1,")")),
               y = expression(paste("ETR")))+
  theme(legend.position = "top")
PI.curves
dev.off()

```


#PLATE 5

# Import data
```{r import_data}
Data <-read.csv("RAnalysis/data/ImagingPam/20230510_Spat_Plate5.csv", header=T, sep=";", na.string="NA") #reads in the data files
Data <- Data[, c("Date", "Time", "PAR", "ETR1","ETR2","ETR3","ETR4","ETR5","ETR6","ETR7","ETR8","ETR9","ETR10","ETR11",
      "ETR12","ETR13","ETR14","ETR15","ETR16","ETR17","ETR18",
      "ETR19","ETR20","ETR21","ETR22")]
# change format from wide to long
Data <- Data %>%  pivot_longer(., cols = starts_with("ETR"), names_to = "Spat.ID")
Data$value <- na_if(Data$value, 0)
#need to Remove all data at PAR values above where ETR hits zero
Data$PAR <- as.numeric(Data$PAR)
colnames(Data)[5] ="ETR"

```


# View Data plots
```{r}
Data %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point()+
  theme_bw()
```

```{r}
set.seed(123)
Data.PI  <- Data %>% subset(PAR<900) 
curve.nlsPIC <- Data.PI %>% nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))
coef(curve.nlsPIC)
plot(ETR ~ PAR, data = Data.PI)
lines(0:900,
      predict(curve.nlsPIC,
              newdata = data.frame(PAR = 0:900)))
```
# Define PI curve function as a nonlinear Least Squares regression of a quadratic fit, test nls fit
Aquatic Photosynthesis, Falkowski   
Pmax = max photosynthesis (AKA Am from Bayesian script)  
alpha = quantum yeild (AKA AQY from Bayesian script)  
I/E = irradiance (AKA PAR from Bayesian script)  
Rd = dark respiration   

Using fixed initial values  
```{r}

Data.PI <- Data.PI %>% subset(Spat.ID!="ETR10")
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR16"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR4"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR7"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR4"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR6"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR9"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR18"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR19"))

nls_data5 <- Data.PI %>%
group_by(Spat.ID) %>%
nest(-Spat.ID) %>%
mutate(model1 = map(data, ~
nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4)) %>%
tidy %>%
dplyr::select(term, estimate) %>%
spread(term, estimate))) %>%
unnest(model1) %>%
mutate(Ik = Am/AQY)%>%
mutate(Date = "20230510") %>%
mutate(Plate = "Plate5") %>%
mutate(Spat.ID.PAM = paste0(Date,"_",Plate,"_",Spat.ID)) %>%
write_csv(., "RAnalysis/output/Plate5_pi_curve_pars_NLS_fixedparms.csv")
```

Plot curve over data points.  
```{r}
augmented <- Data.PI %>%
  filter(PAR <900) %>%
  nest(-Spat.ID) %>% 
  mutate(
    fit = map(data, ~ nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))),
    augmented = map(fit, augment),
  ) %>% 
  unnest(augmented)

augmented$ID <-augmented$Spat.ID
Aug <- augmented %>% separate(ID, c("Sp", "Num", "Type"))

#all colonies together
pdf("RAnalysis/output/Plate5_PI_Curve_Fit_Plots.pdf")
PI.curves <- Aug %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point() + 
  geom_line(aes(y=.fitted, x=PAR,group=Spat.ID))+
  theme_classic()+
          labs(x = expression(paste('PAR (', mu, "mol photons m"^-2, 's'^-1,")")),
               y = expression(paste("ETR")))+
  theme(legend.position = "top")
PI.curves
dev.off()

```


#PLATE 6

# Import data
```{r import_data}
Data <-read.csv("RAnalysis/data/ImagingPam/20230510_Spat_Plate6.csv", header=T, sep=";", na.string="NA") #reads in the data files
Data <- Data[, c("Date", "Time", "PAR", "ETR1","ETR2","ETR3","ETR4","ETR5","ETR6","ETR7","ETR8","ETR9","ETR10","ETR11",
      "ETR12","ETR13","ETR14","ETR15","ETR16","ETR17","ETR18",
      "ETR19","ETR20","ETR21")]
# change format from wide to long
Data <- Data %>%  pivot_longer(., cols = starts_with("ETR"), names_to = "Spat.ID")
Data$value <- na_if(Data$value, 0)
#need to Remove all data at PAR values above where ETR hits zero
Data$PAR <- as.numeric(Data$PAR)
colnames(Data)[5] ="ETR"

```


# View Data plots
```{r}
Data %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point()+
  theme_bw()
```

```{r}
set.seed(123)
Data.PI  <- Data %>% subset(PAR<900) 
curve.nlsPIC <- Data.PI %>% nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))
coef(curve.nlsPIC)
plot(ETR ~ PAR, data = Data.PI)
lines(0:900,
      predict(curve.nlsPIC,
              newdata = data.frame(PAR = 0:900)))
```
# Define PI curve function as a nonlinear Least Squares regression of a quadratic fit, test nls fit
Aquatic Photosynthesis, Falkowski   
Pmax = max photosynthesis (AKA Am from Bayesian script)  
alpha = quantum yeild (AKA AQY from Bayesian script)  
I/E = irradiance (AKA PAR from Bayesian script)  
Rd = dark respiration   

Using fixed initial values  
```{r}

Data.PI <- Data.PI %>% subset(Spat.ID!="ETR12")
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR18"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR21"))
Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR3"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR4"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR6"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR9"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR18"))
#Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR19"))

nls_data6 <- Data.PI %>%
group_by(Spat.ID) %>%
nest(-Spat.ID) %>%
mutate(model1 = map(data, ~
nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4)) %>%
tidy %>%
dplyr::select(term, estimate) %>%
spread(term, estimate))) %>%
unnest(model1) %>%
mutate(Ik = Am/AQY)%>%
mutate(Date = "20230510") %>%
mutate(Plate = "Plate6") %>%
mutate(Spat.ID.PAM = paste0(Date,"_",Plate,"_",Spat.ID)) %>%
write_csv(., "RAnalysis/output/Plate6_pi_curve_pars_NLS_fixedparms.csv")
```

Plot curve over data points.  
```{r}
augmented <- Data.PI %>%
  filter(PAR <900) %>%
  nest(-Spat.ID) %>% 
  mutate(
    fit = map(data, ~ nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))),
    augmented = map(fit, augment),
  ) %>% 
  unnest(augmented)

augmented$ID <-augmented$Spat.ID
Aug <- augmented %>% separate(ID, c("Sp", "Num", "Type"))

#all colonies together
pdf("RAnalysis/output/Plate6_PI_Curve_Fit_Plots.pdf")
PI.curves <- Aug %>%
ggplot(aes(x=PAR, y=ETR, color=Spat.ID))+
  geom_point() + 
  geom_line(aes(y=.fitted, x=PAR,group=Spat.ID))+
  theme_classic()+
          labs(x = expression(paste('PAR (', mu, "mol photons m"^-2, 's'^-1,")")),
               y = expression(paste("ETR")))+
  theme(legend.position = "top")
PI.curves
dev.off()

```







```{r}
PI.params <- rbind(nls_data1, nls_data2, nls_data3, nls_data4, nls_data5, nls_data6)

PI.params <- PI.params[,-2]

# change format from wide to long
PI.params <- PI.params %>%  pivot_longer(., cols = Am:Ik, names_to = "metric", values_to = "value")

PI.params <- PI.params %>% subset(metric!="Rd")

PI.params$Spat.ID.PAM <- paste0(PI.params$Date, "_", PI.params$Plate, "_", PI.params$Spat.ID) 
PI.params <- left_join(PI.params, sample.info, by="Spat.ID.PAM")

PI.params <- PI.params %>%
  subset(Type!="Algae")
  
ggplot(data = PI.params, aes(x = Size.mm2, y = value)) +
  geom_point() +
  facet_wrap(~metric, scales = "free_y")
```

Remove Outliers
```{r}
Am <- PI.params %>%
  subset(metric=="Am") %>%
  subset(value<80) %>%
  subset(Size.mm2<6)

AQY <- PI.params %>%
  subset(metric=="AQY") %>%
  subset(Size.mm2<6)

Ik <- PI.params %>%
  subset(metric=="Ik") %>%
  subset(value<250) %>%
  subset(Size.mm2<6)

PI.params <- rbind(Am,AQY,Ik)

ggplot(data = PI.params, aes(x = Size.mm2, y = value)) +
  geom_point() +
  facet_wrap(~metric, scales = "free_y")

write_csv(PI.params, "RAnalysis/output/PI.params.csv")

```

Plot metrics as a function of Spat Area
```{r}

ggplot(data = PI.params, aes(x = Size.mm2, y = value)) +
  geom_point() +
  stat_poly_line() +
  stat_poly_eq(use_label(c("eq", "R2","P")), size = 2.5) +
  facet_wrap(~metric, scales = "free_y") +
  theme_classic()

```

Plot metrics as a function of Polyp Number
```{r}
ggplot(data = PI.params, aes(x = Polyp.Number, y = value)) +
  stat_poly_line() +
  stat_poly_eq(use_label(c("eq", "R2","P")), size = 2.5) +
  geom_point() +
  facet_wrap(~metric, scales = "free_y")+
  theme_classic()
```
